The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Minor edits to paper

@@

o10 = true
\end{MyVerbatim}
}
\medspace
We also briefly describe the algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other (in which case, the $F$-pure threshold is just the minimum of the $1/a_i$ as mentioned above).  Recall that a set of elements $\{f_i\}$ are said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.  We verify this by looking at the jacobian matrix of each the subsets of the $f_i$ (evaluated at the origin) and checking that these matrices have the expected rank.  We also verify that these subsets generate ideals of the correct height.  Note, this calls {\tt factor f}, which may be slow.  The user can turn off this factorization call with {\tt UseSpecialAlgorithms => false}.

To verify whether $f$ factors into simple normal crossing factors, the function {\tt isSimpleNormalCrossing} is called.  This function is also exposed to the user.  Note, if one sets the {\tt IsLocal => true} option, the {\tt isSimpleNormalCrossing} function checks that the $f_i$ are in simple normal crossing everywhere, which can be much slower (as jacobian ideals are computed).

@@

{\color{red}  Point out for people interested in computing log canonical thresholds:  Zhixian Zhou apparently proved in her thesis that the $F$-pure threshold for hypersurfaces is always a lower bound for the log canonical threshold.  Therefore, this package effectively computes such lower bounds, and is much faster than the \emph{Dmodules} package, which appears to be the only package in Macaulay2 that computes log canonical thresholds.}

>>>>

%This is for Karl
{\color{red}  Point out for people interested in computing log canonical thresholds:  Zhixian Zhou apparently proved in her thesis that the $F$-pure threshold for hypersurfaces is always a lower bound for the log canonical threshold.  Therefore, this package effectively computes such lower bounds, and is much faster than the \emph{Dmodules} package, which appears to be the only package in Macaulay2 that computes log canonical thresholds.}

@@

o10 = true
\end{MyVerbatim}
}
\medspace

If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the three forementioned cases, then the function {\tt fpt} next checks whether the polynomial $f$ has simple normal crossings, in which case its $F$-pure threshold is easily computed.

We briefly describe the algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other, in which case, the $F$-pure threshold is just the minimum of the $1/a_i$. Recall that a set of elements $\{f_i\}$ is said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.  The functionality verifies this by computing the Jacobian matrix of each subset of the $f_i$ (evaluated at the origin), and checking that these matrices have the expected rank.  It is also verified that these subsets generate ideals of the correct height.  Note that {\tt factor f} is called, which may be slow.  The user can avoid this factorization call by setting {\tt UseSpecialAlgorithms} to {\tt false}.

This method for determining whether $f$ is in simple normal crossing is implemented in the function {\tt isSimpleNormalCrossing}, which is also exposed to the user.
Note that if one sets the option {\tt IsLocal} for this function to {\tt true}, then {\tt isSimpleNormalCrossing} checks that the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower (as Jacobian ideals are computed).

@@
